Lattice model

### 2017-04-03 oopsla17/lattice-model.tex
typo
Get rid of predicate Fin

\begin{defn}{(\emph{Offset subspace})}
  An $N$-dimenaional \emph{offset subspace} is a finite Cartesian product of $N$
  subsets of $\zinf{}$. The set of $N$-dimensional offset subspaces is written
  ${\mathcal{P}(\zinf{})}^N$.

  A offset spaces can be \emph{projected} in the $i^{\textit{th}}$ dimension by
  $\pi_i : {\mathcal{P}(\zinf{})}^N \to \mathcal{P}(\zinf{})$ where $i \in
  \mathsf{Fin}(N)$.
\end{defn}

\begin{defn}{(\emph{Subscript})}
  An $N$-dimensional offset subspace $S$ is called a \emph{subscript} if it
  satisfies:
%
  \begin{equation*}
    \forall i \in \textsf{Fin}(N).\
      \pi_i (S) = \{p\} \wedge p \in \mathbb{Z}
      \vee
      \pi_i (S) = \interv{-\infty}{\infty}{\mathsf{true}}
  \end{equation*}
  %
  That is, the $i^{th}$ component of the set is either a singleton
  in $\mathbb{Z}$ or the infinite interval.

>>>>

\begin{defn}{(\emph{Offset subspace})}
  An $N$-dimensional \emph{offset subspace} is a finite Cartesian product of $N$
  subsets of $\zinf{}$. The set of $N$-dimensional offset subspaces is written
  ${\mathcal{P}(\zinf{})}^N$.

  A offset spaces can be \emph{projected} in the $i^{\textit{th}}$ dimension by
  $\pi_i : {\mathcal{P}(\zinf{})}^N \to \mathcal{P}(\zinf{})$ where $1 \leq i
  \leq N$.
\end{defn}

\begin{defn}{(\emph{Subscript})}
  An $N$-dimensional offset subspace $S$ is called a \emph{subscript} if it
  satisfies:
%
  \begin{equation*}
    \forall i.\ 1 \leq i \leq N \implies
      \pi_i (S) = \{p\} \wedge p \in \mathbb{Z}
      \vee
      \pi_i (S) = \interv{-\infty}{\infty}{\mathsf{true}}
  \end{equation*}
  %
  That is, the $i^{th}$ component of the set is either a singleton
  in $\mathbb{Z}$ or the infinite interval.
